CLT Results

### 2022-03-30 analysis/clt_irt_analysis.Rmd
add aoa to freq model

format <- l.format%>%left_join(names)

# plot chart
ggplot(format, aes(Theta, P.1)) + 
  geom_line() + 
  #ggtitle('Probability Tracelines') + 
  xlab(expression(theta)) + 
  ylab(expression(P(theta))) + 
  facet_wrap(~targetWord)+
  ylim(0,1)+
  #geom_hline(aes(yintercept = 0.5)) +
  theme_bw() + 
  theme(
        axis.text.x=element_text(colour="black"),
        axis.text.y=element_text(colour="black"),
        legend.title=element_blank())
```
```{r}
plot(firt2, type='trace', which.item = c(1:43), facet_items=T, 
     as.table = TRUE, auto.key=list(points=F, lines=T, columns=4, space = 'top', cex = .8), 
              theta_lim = c(-6, 6), 
     main = "")
```

>>>>

format <- l.format%>%left_join(names)%>%left_join(aoa)

# plot chart
ggplot(format, aes(Theta, P.1, col = aoa_german_comb, group = item)) + 
  geom_line() + 
  #ggtitle('Probability Tracelines') + 
  xlab(expression(theta)) + 
  ylab(expression(P(theta))) + 
  #facet_wrap(~targetWord)+
  ylim(0,1)+
  scale_color_viridis_c(name = "AoA") +
  #geom_hline(aes(yintercept = 0.5)) +
  theme_bw() + 
  theme(
        axis.text.x=element_text(colour="black"),
        axis.text.y=element_text(colour="black"),
        legend.title=element_blank())
```
```{r}
plot(firt2, type='trace', which.item = c(1:43), facet_items=T, 
     as.table = TRUE, auto.key=list(points=F, lines=T, columns=4, space = 'top', cex = .8), 
              theta_lim = c(-6, 6), 
     main = "")
```
